---
title: "fars functions"
author: "Barnabe"
date: "26/01/2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This code is part of an assignment from "Buiding R Packages" at Coursera. <http://www.coursera.org>.

Its main functions are `fars_summarise_year` and `fars_map_state` which allo users to produce descriptibe statistics of U.S. traffic accidents by year and month for the former, and to visualise traffic accidents in a given state and year on a simple contour map for the latter. 

Data from 2013 to 2015 is available.

## Summary statistics

This is an example for 2013 to 2015: `fars_summarize_years(c(2013:2015))`

```{r sumarise, echo=FALSE}
library(fars)
suppressMessages(require(dplyr))
source(file="R/fars_functions.R")
fars_summarize_years(c(2013:2015))
```

## Mapping traffic accidents

This is an example for Florida in 2013: `fars_map_state("12","2013")`

```{r map, echo=FALSE}
library(maps)
fars_map_state("12","2013")
```

